Casual Bandits

### 2016-01-12 causal-bandit/icml-2015/causal-bandits-icml.tex
adds figures from simple regret experiment
adds figures

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DISCUSSION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

>>>>

\begin{figure}
\caption{Simple regret vs horizon, $T$, for $N = 30$ for UCB with $\alpha=2$, Causal-Best-Arm-Identification with $m=2$ and Causal-Best-Arm-Identification with $m=N$. Error bars show estimated 95\% confidence interval from 1000 simulations.}
\label{fig:simple_vs_T}
\centering
\includegraphics[width=.5\textwidth]{exp_simpleregret_vs_T_N30_sims1000_20160113_010512.pdf}
\end{figure}

\begin{figure}
\caption{Simple regret vs number of variables, $N$, for $T=500$, for UCB with $\alpha=2$, Causal-Best-Arm-Identification with $m=2$ and Causal-Best-Arm-Identification with $m=N$. Error bars show estimated 95\% confidence interval from 1000 simulations.}
\label{fig:simple_vs_N}
\centering
\includegraphics[width=.5\textwidth]{exp_simpleregret_vs_N_T500_sims1000_20160113_010511.pdf}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DISCUSSION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
